It's Never Too Late To Learn\\ \emph{Using Online Machine Learning in Distributed Systems}

### 2016-01-22 writeups/msr_workshop/paper.tex
more content

\section{Using Online Learning in Distributed Systems}

@@

\ignore{
\section{Expanding the scope}

There are two drawbacksTwo drawbacks: opacity and scope.

Opacity (also, which features matter?)
- We are also pursuing work on cracking models open to see what they are doing inside.
There are different ways to gain insight as to what a model is doing. For example a simple
linear model may learn a vector of weights on the supplied features. These weights can be
studied, and indeed some techniques such as lasso are oftne used to reduce the number of features. However, these
techniques need to be handled carefully. Just becasue a feature has 0 weight doesn't mean it
can be removed: perhaps it is unimportant preceisely because it exists, and its removal all of
asudden changes the weight on other features.
}

>>>>

\section{Challenges}

@@

\section{Drawbacks}

The approach we have outlined above has at least two drawbacks. One is that we
are using machine-learned models to capture the complexity of a distributed
systems decision. This means that the resulting optimal policy will be opaque to
us, making it difficult to discover what contextual information matters, for
example.  We are independently pursuing work in cracking models open to see what
can be learned from them, but in general this is not always possible nor is it
reliable to draw conclusion from things like learned weights. In effect, our
position is to accept this opacity as the cost of offloading the complexity of
making the right decision to the learning system.

The second drawback is that our proposal only replaces hand-designed policies at
existing decision points. In other words, machine learning is used as an
alternative policy within an existing design and architecture. Can machine
learning influence the design/architecture of the system itself? Systems like
the Decision Service advocate the former approach, but it is conceivable that in
the future distributed systems will be co-designed based on learning objectives.

\ignore{
We are also pursuing work on cracking models open to see what they are doing inside.
There are different ways to gain insight as to what a model is doing. For example a simple
linear model may learn a vector of weights on the supplied features. These weights can be
studied, and indeed some techniques such as lasso are oftne used to reduce the number of features. However, these
techniques need to be handled carefully. Just becasue a feature has 0 weight doesn't mean it
can be removed: perhaps it is unimportant preceisely because it exists, and its removal all of
asudden changes the weight on other features.
}
